---
title: "Tutorial Basics"
author: "Filip Schouwenaars"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial Basics}
  %\VignetteEngine{tutorial::tutorial}
  %\VignetteEncoding{UTF-8}
---

The `tutorial` package is a wrapper around `knitr` that is able to convert your static code chunks into a R/Python editor where people can experiment. This is done with the help of [DataCamp Light](https://www.github.com/datacamp/datacamp-light), a JavaScript library that converts HTML chunks with the proper formatting into iframes that house an interactive R or Python session.

This vignette will discuss two ways of using the `tutorial` package: to create interactive 'fiddles' and to create fully-fledged coding exercise right inside your browser.

## Fiddles

Suppose you coded an R code example in R Markdown as follows:

    ```{r eval = FALSE}
    a <- 2
    b <- 3
    ```

You can convert this code chunk into a fiddle to experiment. First add an `ex` and `type` option:

    ```{r ex="play_around", type="sample-code"}
    a <- 2
    b <- 3
    ```
    
and then call the render function on your R markdown file:

```{r eval = FALSE}
library(tutorial)
tutorial::render("my_doc.Rmd")
```

The resulting HTML file will contain an iframe that looks like this, where people can experiment. On the left, there is a script editor. When you hit Run, your code is executed in the console on the right. You can also directly experiment inside this console.

```{r eval = FALSE, include = FALSE, ex="play_around", type="sample-code"}
a <- 2
b <- 3
```

To not clutter the code example, you might want to pre-load some data or load some packages beforehand. You can do this by specifying a chunk with `type = 'pre-exercise-code'`. Make sure you specify the same `ex` label to tie the `pre-exercise-code` to the correct `sample-code`:

    ```{r ex="play_around", type="sample-code"}
    c <- 4
    library(dplyr)
    ```
    

## Interactive exercises

Next to fiddles, you can also code up entire interactive exercises with DataCamp Light. This group of code chunks:

    ```{r ex="create_a", type="pre-exercise-code"}
    b <- 5
    ```
    
    ```{r ex="create_a", type="sample-code"}
    # Create a variable a, equal to 5
    
    
    # Print out a
    
    ```
    
    ```{r ex="create_a", type="solution"}
    # Create a variable a, equal to 5
    a <- 5
    
    # Print out a
    a
    ```
    
    ```{r ex="create_a", type="sct"}
    test_object("a")
    test_output_contains("a", incorrect_msg = "Make sure to print `a`")
    success_msg("Great!")
    ```
    
Converts to the following DataCamp Light exercise. The `pre-exercise-code` initializes the R session. The `sample-code` is the fill-in form to start from, The `solution` specifies the solution, and finally `sct` stands for Submission Correctness Test. These tests to check whether the student submitted the correct code, can be written with the [`testwhat`](https://www.github.com/datacamp/testwhat) package.

```{r eval = FALSE, include = FALSE, ex="create_a", type="pre-exercise-code"}
# This code is available in the workspace when the session initializes
b <- 5
```

```{r eval = FALSE, include = FALSE, ex="create_a", type="sample-code"}
# Create a variable a, equal to 5


# Print out a

```

```{r eval = FALSE, include = FALSE, ex="create_a", type="solution"}
# Create a variable a, equal to 5
a <- 5

# Print out a
a
```

```{r eval = FALSE, include = FALSE, ex="create_a", type="sct"}
test_object("a")
test_output_contains("a", incorrect_msg = "Make sure to print `a`")
success_msg("Great!")
```

```{r eval = FALSE, include = FALSE, ex="create_a", type="hint"}
Here is a hint: use `<-` for assignment
```

For more examples on these DataCamp Light exercises, you can visit the text versions of DataCamp's free introduction to R course:

- [Chapter 1: Intro to basics](https://www.datacamp.com/courses/free-introduction-to-r/chapter-1-intro-to-basics-1-r)
- [Chapter 2: Vectors](https://www.datacamp.com/courses/free-introduction-to-r/chapter-2-vectors-2-r)
- [Chapter 3: Matrices](https://www.datacamp.com/courses/free-introduction-to-r/chapter-3-matrices-3-r)
- [Chapter 4: Factors](https://www.datacamp.com/courses/free-introduction-to-r/chapter-4-factors-4-r)
- [Chapter 5: Data Frames](https://www.datacamp.com/courses/free-introduction-to-r/chapter-5-data-frames-r)
- [Chapter 6: Lists](https://www.datacamp.com/courses/free-introduction-to-r/chapter-6-lists-r)

## Python

Although it is somewhat strange to code up Python examples and exercises inside R Markdown, this is perfectly possible; simply replace the `r` in the chunk specification:

```
```{r ex="play_around", type="sample-code"}
```

with `python`:

```
```{python ex="play_around", type="sample-code"}
```

For writing Submission Correctness tests, you can use the [`pythonwhat`](https://www.github.com/datacamp/pythonwhat) package, `testwhat`'s counterpart for Python exercises.
