---
title: "Tutorial Basics"
author: "Filip Schouwenaars"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
tutorial::go_interactive()
```

At DataCamp we build tools to [learn data science](https://www.datacamp.com) interactively. See e.g. our online [R tutorial](https://www.datacamp.com/courses/free-introduction-to-r) to learn R Programming and our Python For Data Science tutorial to [learn Python](https://www.datacamp.com/courses/intro-to-python-for-data-science).

The `tutorial` package by DataCamp is a utility for knitr that is able to convert your static code chunks into an R editor where people can experiment. This is done with the help of [DataCamp Light](https://www.github.com/datacamp/datacamp-light), a JavaScript library that converts HTML chunks with the proper formatting into iframes that house an interactive R session.

This vignette will discuss two ways of using the `tutorial` package: to create interactive 'fiddles' and to create fully-fledged coding exercise right inside your browser.

## Fiddles

Suppose you have a basic R Markdown file that looks as follows:

    ---
    title: "Example Document"
    author: "Your name here"
    output:
      html_document:
        self_contained: false
    ---

    You can create variables with `<-`:
    
    ```{r}
    a <- 2
    b <- 3
    ```

To convert your static code chunk from before into a fiddle to experiment, you have to tell `knitr` to use `tutorial`:

    ---
    title: "Example Document"
    author: "Your name here"
    output:
      html_document:
        self_contained: false
    ---

    ```{r, include=FALSE}
    tutorial::go_interactive()
    ```
    
    You can create variables with `<-`:

    ```{r}
    a <- 2
    b <- 3
    ```
    
If you now render your R Markdown file, the resulting HTML file will contain an iframe:

```{r}
a <- 2
b <- 3
```

On the left, there is a script editor. When you hit Run, your code is executed in the console. You can also directly experiment inside this console.

To not clutter the code example, you might want to pre-load some data or load some packages beforehand. You can do this by specifying a chunk with `type = 'pre-exercise-code'`. You need both `ex` and `type` options in your chunk objects to tie the two code chunks together:

    ```{r ex="play_around", type="pre-exercise-code"}
    c <- 4
    library(stringr)
    ```
    
    ```{r ex="play_around", type="sample-code"}
    a <- 2
    b <- 3
    ```

```{r ex="play_around", type="pre-exercise-code"}
c <- 4
library(stringr)
```

```{r ex="play_around", type="sample-code"}
a <- 2
b <- 3
```


## Interactive exercises

Next to fiddles, you can also code up entire interactive exercises with DataCamp Light. This group of code chunks:

    ```{r ex="create_a", type="pre-exercise-code"}
    b <- 5
    ```
    
    ```{r ex="create_a", type="sample-code"}
    # Create a variable a, equal to 5
    
    
    # Print out a
    
    ```
    
    ```{r ex="create_a", type="solution"}
    # Create a variable a, equal to 5
    a <- 5
    
    # Print out a
    a
    ```
    
    ```{r ex="create_a", type="sct"}
    test_object("a")
    test_output_contains("a", incorrect_msg = "Make sure to print out `a`.")
    success_msg("Great!")
    ```
   
Converts to the following DataCamp Light exercise:

```{r ex="create_a", type="pre-exercise-code"}
b <- 5
```

```{r ex="create_a", type="sample-code"}
# Create a variable a, equal to 5


# Print out a

```

```{r ex="create_a", type="solution"}
# Create a variable a, equal to 5
a <- 5

# Print out a
a
```

```{r ex="create_a", type="sct"}
test_object("a")
test_output_contains("a", incorrect_msg = "Make sure to print out `a`.")
success_msg("Great!")
```

The `pre-exercise-code` initializes the R session. The `sample-code` is the fill-in form to start from, The `solution` specifies the solution, and finally `sct` stands for Submission Correctness Test. These tests to check whether the student submitted the correct code, can be written with the functions from the [`testwhat`](https://www.github.com/datacamp/testwhat) package.

For more examples on these DataCamp Light exercises, you can visit the text versions of DataCamp's free introduction to R course:

- [Chapter 1: Intro to basics](https://www.datacamp.com/courses/free-introduction-to-r/chapter-1-intro-to-basics-1-r)
- [Chapter 2: Vectors](https://www.datacamp.com/courses/free-introduction-to-r/chapter-2-vectors-2-r)
- [Chapter 3: Matrices](https://www.datacamp.com/courses/free-introduction-to-r/chapter-3-matrices-3-r)
- [Chapter 4: Factors](https://www.datacamp.com/courses/free-introduction-to-r/chapter-4-factors-4-r)
- [Chapter 5: Data Frames](https://www.datacamp.com/courses/free-introduction-to-r/chapter-5-data-frames-r)
- [Chapter 6: Lists](https://www.datacamp.com/courses/free-introduction-to-r/chapter-6-lists-r)

