---
title: "Example Document"
author: "Your name here"
output:
  html_document:
    self_contained: false
---

```{r, include=FALSE}
tutorial::go_interactive()
```

You can use the `tutorial` package to convert static code chunks into 'fiddles', i.e. editors where people can experiment with your code. If you specify the `ex` and `type` properties, `tutorial` knows what to do:

```{r}
a <- 2
b <- 3

a + b
```

You can also create interactive exercises right inside your R Markdown document. Suppose you want to explain people how variable assignment works in R. Create an exercise with a certain identifier, `create_a` in this case. Then, in different R code chunks, specify the elements of the exercise by setting the `type` inside the code chunk options.

```{r ex="create_a", type="pre-exercise-code"}
b <- 5
```

```{r ex="create_a", type="sample-code"}
# Create a variable a, equal to 5


# Print out a

```

```{r ex="create_a", type="solution"}
# Create a variable a, equal to 5
a <- 5

# Print out a
a
```

```{r ex="create_a", type="sct"}
test_object("a")
test_output_contains("a", incorrect_msg = "Make sure to print `a`.")
success_msg("Great!")
```

