---
title: "Example Document"
author: "Your name here"
output: html_document
---

You can use the `tutorial` package to convert static code chunks into 'fiddles', i.e. editors where people can experiment with your code. If you specify the `ex` and `type` properties, `tutorial` knows what to do:

```{r, ex="play_around", type="sample-code"}
a <- 2
b <- 3

a + b
```

You can also create interactive exercises right inside your R Markdown document. Suppose you want to explain people how variable assignment works in R. Create an exercise with a certain identifier, `create_a` in this case. Then, in different R code chunks, specify the elements of the exercise by setting the `type` inside the code chunk options.

```{r, ex="create_a", type="pre-exercise-code"}
# This code is available in the workspace when the session initializes
b <- 5
```

```{r, ex="create_a", type="sample-code"}
# Create a variable a, equal to 5


# Print out a

```

```{r, ex="create_a", type="solution"}
# Create a variable a, equal to 5
a <- 5

# Print out a
a
```

```{r, ex="create_a", type="sct"}
test_object("a")
test_output_contains("a", incorrect_msg = "Make sure to print `a`")
success_msg("Great!")
```

```{r, ex="create_a", type="hint"}
Here is a hint: use `<-` for assignment
```

DataCamp Light also supports Python exercises. Let's create an exercise with a certain identifier, `create_b` in this case. Then, in different Python code chunks, specify the elements of the exercise by setting the `type` inside the code chunk options.

```{python, ex="create_b", type="pre-exercise-code"}
```

```{python, ex="create_b", type="sample-code"}
# Create a variable b, equal to 4

```

```{python, ex="create_b", type="solution"}
# Create a variable b, equal to 4
b = 4
```

```{python, ex="create_b", type="sct"}
test_object("b")
success_msg("Great!")
```

```{python, ex="create_b", type="hint"}
Here is a hint: use `=` for assignment.
```

Have fun teaching!

