---
title: "Example Document"
author: "Your name here"
output: html_document
---

This example document shows how you can embed interactive exercises in your R Markdown files.

As an example, suppose youw ant to explain people how variable assignment works in R. Create an exercise with a certain identifier, `create_a` in this case. Then, in different R code chunks, specify the elements of the exercise by setting the `type` inside the code chunk options.

```{r, ex=create_a, type=pre-exercise-code}
# This code is available in the workspace when the session initializes
b <- 5
```

```{r, ex=create_a, type=sample-code}
# Create a variable a, equal to 5


# Print out a

```

```{r, ex=create_a, type=solution}
# Create a variable a, equal to 5
a <- 5

# Print out a
a
```

```{r, ex=create_a, type=sct}
test_object("a")
test_output_contains("a", incorrect_msg = "Make sure to print `a`")
success_msg("Great!")
```

```{r, ex=create_a, type=hint}
Here is a hint: use `<-` for assignment
```

It's perfectly possible to still work with normal R markdown chunks, like this:

```{r}
head(mtcars, 10)
```
